The Birth of a Galaxy: Population III Metal Enrichment and Population II Stellar Populations

### 2010-10-25 science_ms.tex
Merged together eps files into a composite ones to replace the plottwo{} in the apj format.  Fixed the figure filenames to reflect their new figure numbers.
Added sentence in abstract about DLAs.  Removed some discussion about the importance of the merger history since this is already discussed in the results.

\begin{sciabstract}
  Supernova explosions from the first stars in the universe, which are
  predicted to be very massive, chemically enriched the intergalactic
  medium, originally a primordial mix of hydrogen and helium.  A
  fraction of these metals propagate into star-forming regions,
  providing more efficient cooling mechanisms and, in turn, increasing
  gaseous fragmentation in the first stellar clusters.  Here, we
  report on the birth of two high-redshift dwarf galaxies in a
  cosmological radiation hydrodynamics simulation.  We find that only
  one supernova is sufficient to enrich the nearby star-forming gas
  with a floor of 1/1,000 of the solar metallicity ratio, preventing
  any further metal-free star formation within 10 kpc of the past
  explosion.  We follow the entire star formation history of these
  galaxies, providing robust models to interpret the stellar
  populations of nearby dwarf galaxies and future observations of
  high-redshift dwarf galaxies.
\end{sciabstract}

@@

We also find that the merger history plays an important role in
supplying gas into halos after its first epoch of SF.  Mergers of
halos below the filtering mass are inefficient in providing gas
whereas the opposite is true for merging halos above the filtering
mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
significant stellar populations; however SFRs dramatically increase,
and thus metal enrichment, when this threshold is reached.  Halos with
mostly gas-poor mergers or a quiet merger history result in a
monotonic increase in metallicity with time.  SFHs become more complex
with multiple metallicity-age tracks if the halo experiences mergers
with other halos that have an established stellar population.
Furthermore SF that is triggered by blastwaves interacting with
molecular clouds can have metallicities up to a factor of 10 higher
than the main starburst.  Lastly we find that a starburst at $\tvir =
10^4$ K enriches the host halo enough to create a bimodal metallicity
distribution, where the metal-poor component is created before the
burst.  Note that mergers of stellar populations can also create a
similar bimodal distribution.  Such distributions are observed in
dSphs \cite{Battaglia10}.

@@

\clearpage
\begin{figure*}
\includegraphics[width=0.88\textwidth]{f3.eps}
\caption{\label{fig:projections} Density-weighted projections of gas
  density (top), temperature (middle), and metallicity (bottom) at
  $z=7$.  The left column shows the entire simulation volume, where
  the center and right columns focus on the intense and quiet halos,
  which are marked by left and right arrows in the upper-left panel.
  The metallicity projections are a composite picture of metals
  originating from Pop III (red) and Pop II (blue) stars with magenta
  indicating a mixture of the two.}
\end{figure*}

\clearpage
\begin{figure*}
% Need to include f2.eps
\includegraphics[width=0.88\textwidth]{f1.eps}
\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
  stellar mass (middle), and gas fraction (bottom) of the quiet
  (dashed) and intense (solid) halos.  (b) Mass-weighted stellar
  metallicities and gas metallicities enriched by Pop II and Pop III
  SNe of the intense (top) and quiet (bottom) halos.}
\end{figure*}

\clearpage
\begin{figure*}
% Needs f4b.eps
\includegraphics[width=0.88\textwidth]{f4a.eps}
\caption{\label{fig:pops} The scatter plots show the SF history of the
  quiet (left) and intense (right) halos as a function of metallicity
  at $z=7$.  Each circle represents a star cluster, whose area is
  proportional to its mass.  The open circles in the upper right
  represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star clusters.
  The dashed lines in the right panel guide the eye to two stellar
  populations that were formed in two satellite halos, merging at
  $z=7.5$.  The upper histogram shows the SF rate.  The right
  histogram depicts the stellar metallicity distribution.}
\end{figure*}

>>>>

\begin{sciabstract}
  Supernova explosions from the first stars in the universe, which are
  predicted to be very massive, chemically enriched the intergalactic
  medium, originally a primordial mix of hydrogen and helium.  A
  fraction of these metals propagate into star-forming regions,
  providing more efficient cooling mechanisms and, in turn, increasing
  gaseous fragmentation in the first stellar clusters.  Here, we
  report on the birth of two high-redshift dwarf galaxies in a
  cosmological radiation hydrodynamics simulation.  We find that only
  one supernova is sufficient to enrich the nearby star-forming gas
  with a floor of 1/1,000 of the solar metallicity ratio, preventing
  any further metal-free star formation within 10 kpc of the past
  explosion.  This provides a natural explanation for the observed
  floor on damped Lyman alpha (DLA) systems metallicities reported in
  the literature, which is of this order.  We follow the entire star
  formation history of these galaxies, providing robust models to
  interpret the stellar populations of nearby dwarf galaxies and
  future observations of high-redshift dwarf galaxies.
\end{sciabstract}

@@

We also find that the merger history plays an important role in
supplying gas into halos after its first epoch of SF.  Mergers of
halos below the filtering mass are inefficient in providing gas
whereas the opposite is true for merging halos above the filtering
mass.  
% Halos do not necessarily need $\tvir \ge 10^4$ K to form significant
% stellar populations; however SFRs dramatically increase, and thus
% metal enrichment, when this threshold is reached.  Halos with mostly
% gas-poor mergers or a quiet merger history result in a monotonic
% increase in metallicity with time.  SFHs become more complex with
% multiple metallicity-age tracks if the halo experiences mergers with
% other halos that have an established stellar population.  Furthermore
% SF that is triggered by blastwaves interacting with molecular clouds
% can have metallicities up to a factor of 10 higher than the main
% starburst.
Starbursts at $\tvir = 10^4$ K can enrich the host halo enough to
create a bimodal metallicity distribution, where the metal-poor
component is created before the burst.  Note that mergers of stellar
populations can also create a similar bimodal distribution.  Such
distributions are observed in dSphs \cite{Battaglia10}.

@@

\clearpage
\begin{figure*}
\includegraphics[width=\textwidth]{f1.eps}
\caption{\label{fig:projections} Density-weighted projections of gas
  density (top), temperature (middle), and metallicity (bottom) at
  $z=7$.  The left column shows the entire simulation volume, where
  the center and right columns focus on the intense and quiet halos,
  which are marked by left and right arrows in the upper-left panel.
  The metallicity projections are a composite picture of metals
  originating from Pop III (red) and Pop II (blue) stars with magenta
  indicating a mixture of the two.}
\end{figure*}

\clearpage
\begin{figure*}
% Need to include f2.eps
\includegraphics[width=\textwidth]{f2.eps}
\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
  stellar mass (middle), and gas fraction (bottom) of the quiet
  (dashed) and intense (solid) halos.  (b) Mass-weighted stellar
  metallicities and gas metallicities enriched by Pop II and Pop III
  SNe of the intense (top) and quiet (bottom) halos.}
\end{figure*}

\clearpage
\begin{figure*}
\includegraphics[width=\textwidth]{f3.eps}
\caption{\label{fig:pops} The scatter plots show the SF history of the
  quiet (left) and intense (right) halos as a function of metallicity
  at $z=7$.  Each circle represents a star cluster, whose area is
  proportional to its mass.  The open circles in the upper right
  represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star clusters.
  The dashed lines in the right panel guide the eye to two stellar
  populations that were formed in two satellite halos, merging at
  $z=7.5$.  The upper histogram shows the SF rate.  The right
  histogram depicts the stellar metallicity distribution.}
\end{figure*}
